conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-23 paper/paper.Rmd
improved wording

We provide functions for model fitting at various use cases. Further detail for each of the following functions can be seen at: https://idem-lab.github.io/conmat/dev/

* `fit_single_contact_model()`
    * Fits a generalised additive model (GAM) using contact survey data and population size information. This function is recommended for when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.

>>>>

We provide functions for model fitting at various use cases. Further detail for each of the following functions are available at: https://idem-lab.github.io/conmat/dev/

* `fit_single_contact_model()`
    * Fits a generalised additive model (GAM) using contact survey data and population size information. This function is recommended when you want to fit a model to only one setting, for which you might want to provide your own contact survey data.
